---
title: "Toronto Marriage Licenses"
subtitle: "My subtitle if needed"
author: 
  Parth Samant
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

Citations: @opendatatoronto, @R


```{r}
#### Workspace setup ####
library(tidyverse)

#### Simulate data ####
df <- 
  tibble(
    date = seq(as.Date('2023/01/01'), as.Date('2023/12/31'), by="day"),
    num_marriages = rpois(365, lambda = 10)
  )

```



```{r}

# download data
#### Workspace setup ####
library(opendatatoronto)
# [...UPDATE THIS...]

# get package
package <- show_package("e28bc818-43d5-43f7-b5d9-bdfb4eda5feb")
package

# get all resources for this package
resources <- list_package_resources("e28bc818-43d5-43f7-b5d9-bdfb4eda5feb")

# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))

# load the first datastore resource as a sample
data <- filter(datastore_resources, row_number()==1) %>% get_resource()
data



#### Save data ####
# [...UPDATE THIS...]
# change the_raw_data to whatever name you assigned when you downloaded it.
write_csv(data, "data/raw_data/Marriage License Statistics Data.csv") 

```


```{r}
# tests
data <- read_csv("data/raw_data/Marriage License Statistics Data.csv")

# Tests for Negative numbers (LOOK ON CHAPTER 2)

data$MARRIAGE_LICENSES |> min() >= 0

# Tests for NAs

all(is.na(data$MARRIAGE_LICENSES))
```

```{r}

# cleaning 

#### Clean data ####
raw_data <- read_csv("data/raw_data/Marriage License Statistics Data.csv")

cleaned_data <-
  raw_data |>
  janitor::clean_names() |> 
  separate(col = time_period, 
           into = c("year", "month"),
           sep = "-") |>
  mutate(date = lubridate::ymd(paste(year, month, "01", sep = "-")))

#### Save data ####
write_csv(cleaned_data, "data/raw_data/Marriage License Statistics Data.csv")

```


```{r}

ggplot(data = cleaned_data , aes(x= month, y = marriage_licenses)) + geom_point()

```
# Paragraph 

This graph shows the overall number of marriage licenses in certain Toronto boroughs by the month.
There is a positive correlation between the summer months (i.e., June, July, August) and the number of marriage licenses. This correlation was shown using data from @opendatatoronto and mapped in @R. 





# References

@opendatatoronto{,
    title = {opendatatoronto: Access the City of Toronto Open Data Portal},
    author = {Sharla Gelfand},
    year = {2022},
    note = {R package version 0.1.5},
    url = {https://CRAN.R-project.org/package=opendatatoronto},
  }
  
@R{,
    title = {R: A Language and Environment for Statistical Computing},
    author = {{R Core Team}},
    organization = {R Foundation for Statistical Computing},
    address = {Vienna, Austria},
    year = {2024},
    url = {https://www.R-project.org/},
  }